Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-19 numerical-ppm.tex
Many minor changes.  No more undefined references!  Added appendix file.

We first construct monotonic piecewise 
parabolic (third order) interpolations in one dimension
for each of $p$, $\rho$, and $v$  The pressure is determined from
eq.~(\ref{eq:state}), the equation of state.
%We have dropped the subscript b in this and the following two sections because we will be referring solely to baryonic quantities.  
The interpolation formula for some quantity $q$ is given by:
%
\begin{eqnarray}
q_j(x) & = &  q_{L,j} + \tilde{x}(\Delta q_j + q_{6,j}(1-\tilde{x})), \\
\tilde{x}      & \equiv & {x - x_{j-1/2} \over \Delta x_j}, \qquad
             x_{j-1/2} \leq x \leq x_{j+1/2}. \nonumber
\end{eqnarray}
%
This is eq.~(1.4) of CW84 (in the radial rather than mass coordinate as is appropriate for the direct rulerian approach). 
%The zones edges in the mass coordinates are $m_{j-1/2}$ and $m_{j+1/2}$ for the left and right edges, respectively.  
The quantities $q_{L,j}$, $\Delta q_j$,
and $q_{6,j}$ can be viewed simply as interpolation constants; however,
they also have more intuitive meanings.  For example, $q_{L,j}$ is the
value of $q$ at the left edge of zone j, while $\Delta q_j$ and $q_{6,j}$ are analogous to the slope and first order correction to the slope of $q$ (see \citet{1984JCoPh..54..174C} for a complete discussion):
\begin{equation}
\Delta q_j \equiv q_{R,j} - q_{L,j} \qquad 
q_{6,j}    \equiv 6\left[q_j - 1/2\left(q_{L,j} + q_{R,j}\right)\right].
\end{equation}

>>>>

We first construct monotonic piecewise 
parabolic (third order) interpolations in one dimension
for each of $p$, $\rho$, and $v$  The pressure is determined from
eq.~(\ref{eq:eq_of_state}), the equation of state.
%We have dropped the subscript b in this and the following two sections because we will be referring solely to baryonic quantities.  
The interpolation formula for some quantity $q$ is given by:
%
\begin{eqnarray}
q_j(x) & = &  q_{L,j} + \tilde{x}(\Delta q_j + q_{6,j}(1-\tilde{x})), \\
\tilde{x}      & \equiv & {x - x_{j-1/2} \over \Delta x_j}, \qquad
             x_{j-1/2} \leq x \leq x_{j+1/2}. \nonumber
\end{eqnarray}
%
This is eq.~(1.4) of CW84 (in the radial rather than mass coordinate as is appropriate for the direct rulerian approach). 
%The zones edges in the mass coordinates are $m_{j-1/2}$ and $m_{j+1/2}$ for the left and right edges, respectively.  
The quantities $q_{L,j}$, $\Delta q_j$,
and $q_{6,j}$ can be viewed simply as interpolation constants; however,
they also have more intuitive meanings.  For example, $q_{L,j}$ is the
value of $q$ at the left edge of zone j, while $\Delta q_j$ and $q_{6,j}$ are analogous to the slope and first order correction to the slope of $q$ (see \citet{1984JCoPh..54..174C} for a complete discussion):
\begin{equation}
\Delta q_j \equiv q_{R,j} - q_{L,j} \qquad 
q_{6,j}    \equiv 6\left[q_j - 1/2\left(q_{L,j} + q_{R,j}\right)\right].
\end{equation}
